---
title: "hw5"
author: "Ruihan Zhang"
date: "2022-11-16"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(p8105.datasets)
library(viridis)
library(dplyr)
library(purrr)
library(broom)
```

```{r}
homicide= read_csv("./homicide-data.csv") %>% 
  janitor::clean_names() %>% 
  mutate(city_state = str_c(city,",",state))
  
```
There are `r nrow(homicide)` observations. The variables are uid, reported_date, victim_last, victim_first, victim_race, victim_age, victim_sex, city, state, lat, lon, disposition, city_state. The dimension is `r ncol(homicide)` * `r nrow(homicide)`.

```{r}
homicides_number =  homicide %>% 
  group_by(city) %>% 
  summarise(homicides_no = n())
unsolved = homicide %>% 
  group_by(city)  %>% 
  filter(., disposition == "Closed without arrest" | disposition == "Open/No arrest" ) %>% summarise(unsolved_no = n())
sum = merge(homicides_number, unsolved, by = "city")

```

```{r}

sink("test_output")
test = prop.test(x = 1825, n = 2827) 
sink()
tidy = broom::tidy(test)
tidy
```

```{r}
pt = sum %>% 
  mutate(value = map2(unsolved_no, homicides_no, ~ prop.test(.x, .y) %>% 
  tidy())) %>% 
  unnest(value) %>% 
  select(., city, homicides_no, unsolved_no, estimate, conf.low, conf.high)
```

```{r}
 pt %>% 
  mutate(city = fct_reorder(city, estimate)) %>% 
  ggplot(aes(x= city, y = estimate)) +geom_point() + geom_errorbar(aes(ymin = conf.low, ymax = conf.high),width = 0.2) +theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) + labs(title = "the estimates and CIs for each city",
    x = "esitimates",
    y = "confidential interval")
```

```{r}
t_test = function(mu = 0) {
  tt = tibble(rnorm(n = 30, mean = mu, sd = 5))
  
  out = t.test(tt) %>% 
    broom::tidy() %>% 
    select(estimate,p.value)
  
  out
}
     

```

```{r}
mean_df1 = expand_grid(mean = 0, iteration = 1:5000) %>% 
  mutate(out = map(mean,t_test)) %>% 
  unnest(out)
mean_df2 = expand_grid(mean = 1:6, iteration = 1:5000) %>% 
  mutate(out = map(mean,t_test)) %>% 
  unnest(out)

```


```{r}
mean_df2 %>%
  group_by(mean) %>% 
  summarize(mean_estimate = mean(estimate,na.rm = TRUE)) %>% 
  ggplot(aes(x = mean,y = mean_estimate)) +
  scale_x_continuous(limits = c(1,6), breaks = seq(1,6,1)) + 
  geom_point() + geom_path() +
  labs(x = "the true value of μ",y = "the proportion of times the null rejected (the power of the test)",title = "the association between effect size and power")

  
```

When the true value of μ increases, the proportion of times the null rejected (the power of the test) increases. 

```{r}
reject = mean_df2 %>% 
  filter(p.value < 0.05) %>% group_by(mean) %>% 
  summarize(mean_estimate = mean(estimate,na.rm = TRUE)) %>% 
  ungroup()

estimate = mean_df2 %>% 
  group_by(mean) %>% 
  summarize(mean_estimate = mean(estimate,na.rm = TRUE)) %>% 
  ungroup()
  
ggplot(estimate,aes(x = mean, y = mean_estimate)) +
  geom_line(data = estimate ,aes(colour = "estimate mean")) +
  geom_line(data = reject, aes(colour = "reject mean")) +
  geom_point(data = estimate, colour = "purple") +
  geom_point(data = reject,colour = "pink") +
  scale_x_continuous(limits = c(1,6), breaks = seq(1,6,1)) +
  labs(x = "the true value of μ",y = "the average estimate of  μ̂" )

```


As the true value of μ increases, the value of the estimated mean approaches to the value of the rejected mean, because the power increases with increasing effect size. 

